\thetitle

### 2021-03-03 writing/results.tex
removing wes

While most failures to debug scenarios follow the above pattern, a few do not.
Breaking down the reasons for failure for Natural blame (1748 in total)
reveals an additional cause. For a small set of
debugging scenarios (40), Natural produces a run time type error
blaming a non-buggy already typed
component. We tracked down all these cases to known open issues with Typed
Racket and class contracts.

@@

Figure~\ref{fig:effort-comparisons} provides head-to-head comparisons of effort.
To directly compare effort between modes, we compute the difference in trail length between two modes for all scenarios where they both succeed.
Hence, each plot in the figure shows the distribution of scenarios with length differences ranging from -3 (the first mode's trail is 3 steps shorter than the second's) to 3 (the first mode's trail is 3 steps longer than the second's).
The figure offers several insights about the comparative effort for each mode that complement the insights about comparitive success from figure~\ref{fig:avo-bars}.
First, Natural blame never produces shorter trails than Natural exceptions, and sometimes (albeit rarely) produces slightly longer ones.
Second, Natural relatively often (around 10\% of the scenarios) produces shorter trails than both Transient blame modes, and they are sometimes significantly shorter.
Third, Transient last blame often produces shorter trails than Transient first blame, which is a particularly interesting distinction in light of their nearly indistinguishable success rates.
Finally, Transient's blame modes also share the characteristic with Natural that blame sometimes produces longer trails than their corresponding exception modes.

>>>>

While most failures to debug scenarios follow the above pattern, a few do
not.  Breaking down the reasons for failure for Natural blame (1748 in
total) reveals an additional cause. For a small set of debugging scenarios
(40), Natural produces a run time type error blaming a non-buggy already
typed component. All these cases are due to known open issues with Typed
Racket and class contracts.

@@

Figure~\ref{fig:effort-comparisons} provides head-to-head comparisons of
effort.  The effort comparison between modes boils down to the
difference in trail length between two modes for all scenarios where they
both succeed.  Hence, each plot in the figure shows the distribution of
scenarios with length differences ranging from -3 (the first mode's trail
is 3 steps shorter than the second's) to 3 (the first mode's trail is 3
steps longer than the second's).  The figure offers several insights about
the comparative effort for each mode that complement the insights about
comparitive success from figure~\ref{fig:avo-bars}.  First, Natural blame
never produces shorter trails than Natural exceptions, and sometimes
(albeit rarely) produces slightly longer ones.  Second, Natural relatively
often (around 10\% of the scenarios) produces shorter trails than both
Transient blame modes, and they are sometimes significantly shorter.
Third, Transient last blame often produces shorter trails than Transient
first blame, which is a particularly interesting distinction in light of
their nearly indistinguishable success rates.  Finally, Transient's blame
modes also share the characteristic with Natural that blame sometimes
produces longer trails than their corresponding exception modes.
